Generic Cormotif

### 2017-10-17 paper/main.tex
update paper

\begin{assumption} The effects $\beta_1,\beta_2,\ldots,\beta_n$ are independent given $\pi$ and $g$.
\end{assumption}

Here we describe the simplest version of our model. First we assume the effect $\beta_{jr}$ is independent of their standard errors $\hat s_{jr}$. Then by Assumption 1, 2 and 3, we have
\begin{equation}
p(\beta|\pi,g,\hat s) = \prod_{j=1}^np(\beta_j|\pi,g,\hat s) = \prod_{j=1}^n \left [\sum_{k=1}^K\pi_k\prod_{r=1}^R  g_{kr}(\beta_{jr})\right ]
%p(\beta_j|\pi,g,\hat s) = \sum_{k=1}^K\pi_k\prod_{r=1}^R  g_{kr}(\beta_{jr}),
\label{eq:1}
\end{equation}

@@

Another advantage of our generic model is that we could compute the posterior distribution for effects $\beta_{jr}$. By Bayes theorem, we have
\begin{equation}
    p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr}) \propto p(\beta_{jr}|\hat s_{jr})p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})
    \label{eq:5}
\end{equation}

@@

Our method involves three steps:
\begin{enumerate}
    \item For a given $K$, estimate the parameters $\pi$ and $g$ by maximizing the likelihood $L(\pi,g)$, given by (\ref{eq:4}).
    \item Choose the best $K$ by minimizing the Bayesian Information Criterion (BIC).
    \item Compute, for each $j$ and $r$, the posterior distribution $p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr},\hat\pi,\hat g)$ by (\ref{eq:5}).
\end{enumerate}

All the details can be found in Section (\ref{sec:detail}). Step 1 is a convex problem, and we apply a EM algorithm to solve it. Step 2 is straightforward. The conditional distributions $p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr},\hat\pi,\hat g)$ by (\ref{eq:5}) in Step 3 are analytically available, each a mixture of a point mass on zero and $L$ normal distribution.

@@

To measure "significance" of an effect $\beta_{jr}$ we use the local false sign rate ($\lfsr$), which is defined as:
\begin{equation}
    \lfsr_{jr} := \min\{p(\beta_{jr}\geq 0|\hat\beta_{jr},\hat s_{jr},\hat\pi,\hat g), p(\beta_{jr}\leq 0|\hat\beta_{jr},\hat s_{jr},\hat\pi,\hat g)\}
\end{equation}

Intutively, $\lfsr_{jr}$ is the probability that we would get the sign of effect $\beta_{jr}$ incorrect if we were to use our best guess of the sign. Therefore, a small $\lfsr$ indicates high confidence in determining the sign of an effect. Notice that $\lfsr$ is more conservative than the local false discovery rate ($\lfdr$), since we can infer $\lfsr_{jr}\geq\lfdr_{jr}$ from the definition.

@@

For a more general case, suppose
\begin{equation}
g_{kr}(\cdot;w) = \sum_{l=0}^L w_l^{kr}f_l(\cdot),
\label{eq:geng}
\end{equation}
where $f_0$ is a point mass on 0. Then we have 
\begin{equation}
    p(\beta_{jr}|\pi,g,\hat s) = \sum_{k=1}^K\pi_k g_{kr}(\beta_{jr})=  \sum_{k=1}^K\pi_k\sum_{l=0}^Lw_l^{kr}f_l(\beta_{jr})
    = \sum_{l=0}^L\eta_{lr}f_l(\beta_{jr}),
\end{equation}
where $\eta_{lr}=\sum_{k=1}^K\pi_kw_l^{kr}$. Thus, by (\ref{eq:5}), we get
\begin{equation}
    p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr},\pi, g) = \sum_{l=0}^L\theta_{ljr}p_{l}(\beta_{jr}|\hat\beta_{jr},\hat s_{jr}).
\end{equation}
The posterior mixture component $p_l$ is the posterior on $\beta_{jr}$ that would be obtained using prior $f_l(\beta_{jr})$ and likelihood $p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})$. To compute the mixture weights $\theta_{ljr}$, denote
\begin{equation}
    \tilde f_{ljr}(\hat\beta_{jr}) := \int f_l(\beta_{jr})p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})d\beta_{jr},
\end{equation}
the convolution of $f_l$ and a density function. Then $\theta_{ljr}$ can be obtained from
\begin{equation}
    \theta_{ljr} = \frac{\eta_{lr}\tilde f_{ljr}(\hat\beta_{jr})}{\sum_{l'=0}^L\eta_{l'r}\tilde f_{l'jr}(\hat\beta_{jr})}.
\end{equation}

>>>>

%\begin{assumption} The effects $\beta_1,\beta_2,\ldots,\beta_n$ are independent given $\pi$ and $g$.
%\end{assumption}

Here we describe the simplest version of our model. First we assume the effect $\beta_{jr}$ is independent of their standard errors $\hat s_{jr}$. Then by Assumption 1 and 2, we have
\begin{equation}
p(\beta|\pi,g,\hat s) = \prod_{j=1}^np(\beta_j|\pi,g,\hat s) = \prod_{j=1}^n \left [\sum_{k=1}^K\pi_k\prod_{r=1}^R  g_{kr}(\beta_{jr})\right ]
%p(\beta_j|\pi,g,\hat s) = \sum_{k=1}^K\pi_k\prod_{r=1}^R  g_{kr}(\beta_{jr}),
\label{eq:1}
\end{equation}

@@

Another advantage of our generic model is that we could estimate the posterior distribution for effects $\beta_{jr}$, that is $p(\beta_{jr}|\hat\beta,\hat s,\pi,g) $. 
%By Bayes theorem, we have
%\begin{equation}
%    p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr}) \propto p(\beta_{jr}|\hat s_{jr})p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})
%    \label{eq:5}
%\end{equation}

@@

Our method involves three steps:
\begin{enumerate}
    \item For a given $K$, estimate the parameters $\pi$ and $g$ by maximizing the likelihood $L(\pi,g)$, given by (\ref{eq:4}), denote as $\hat\pi$ and $\hat g$.
    \item Choose the best $K$ by minimizing the Bayesian Information Criterion (BIC).
    \item Compute, for each $j$ and $r$, the posterior distribution $p(\beta_{jr}|\hat\beta,\hat s,\hat\pi,\hat g)$.
\end{enumerate}

All the details can be found in Section (\ref{sec:detail}). For Step 1 we apply an EM algorithm to solve it. Step 2 is straightforward. The conditional distributions $p(\beta_{jr}|\hat\beta,\hat s,\hat\pi,\hat g)$ in Step 3 are analytically available, each a mixture of a point mass on zero and $L$ normal distribution.

@@

To measure "significance" of an effect $\beta_{jr}$ we use the local false sign rate ($\lfsr$), which is defined as:
\begin{equation}
    \lfsr_{jr} := \min\{p(\beta_{jr}\geq 0|\hat\beta,\hat s,\hat\pi,\hat g), p(\beta_{jr}\leq 0|\hat\beta,\hat s,\hat\pi,\hat g)\}
\end{equation}

Intuitively, $\lfsr_{jr}$ is the probability that we would get the sign of effect $\beta_{jr}$ incorrect if we were to use our best guess of the sign. Therefore, a small $\lfsr$ indicates high confidence in determining the sign of an effect. Notice that $\lfsr$ is more conservative than the local false discovery rate ($\lfdr$), since we can infer $\lfsr_{jr}\geq\lfdr_{jr}$ from the definition.

@@

For a more general case, suppose
\begin{equation}
g_{kr}(\cdot;w) = \sum_{l=0}^L w_l^{kr}f_l(\cdot),
\label{eq:geng}
\end{equation}
Denote 
\begin{equation}
     \tilde f_{l}(\hat\beta_{jr}) := \int f_l(\beta_{jr})p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})d\beta_{jr},
\end{equation}
as the likelihood of $\hat\beta_{jr}$ if the prior of $\beta_{jr}$ follows $f_l(\beta_{jr})$.

By Bayes theorem, 
\begin{eqnarray}
&&p(\beta_{jr}|\hat\beta,\hat s,\pi, g) = p(\beta_{jr}|\hat\beta_{j},\hat s_j,\pi, g)\nonumber \\
&=& \sum_{k=1}^Kp(\beta_{jr}|\hat\beta_{j},\hat s_j,\pi,g,z_j=k)p(z_j=k|\hat\beta_{j},\hat s_j,\pi, g) \nonumber\\
&=& \sum_{k=1}^Kp(\beta_{jr}|\hat\beta_{jr},\hat s_j,\pi,g,z_j=k)p_{jk}\nonumber \\
&=& \sum_{k=1}^K\frac{p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})g_{kr}(\beta_{jr})}{\int p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})g_{kr}(\beta_{jr})d\beta_{jr}}\times p_{jk} \nonumber\\
&=& \sum_{k=1}^K \frac{\sum_{l=0}^Lw_l^{kr}\tilde f_{l}(\hat\beta_{jr})h_{l}(\beta_{jr}) }{\sum_{l'=0}^Lw_{l'}^{kr}\tilde f_{l'}(\hat\beta_{jr})} \times p_{jk} \nonumber\\
&=& \sum_{l=0}^L \theta_{ljr}h_{l}(\beta_{jr}). 
\end{eqnarray}
Here the posterior mixture component $h_l$ is the posterior on $\beta_{jr}$ that would be obtained using prior $f_l(\beta_{jr})$ and likelihood $p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})$, and the mixture weights $\theta_{ljr}$ is
\begin{equation}
     \theta_{ljr} = \sum_{k=1}^K\frac{w_{l}^{kr}\tilde f_{l}(\hat\beta_{jr})p_{jk}}{\sum_{l'=0}^L\eta_{l'r}\tilde f_{l'jr}(\hat\beta_{jr})}.
\end{equation}

% where $f_0$ is a point mass on 0. Then we have 
% \begin{equation}
%     p(\beta_{jr}|\pi,g,\hat s) = \sum_{k=1}^K\pi_k g_{kr}(\beta_{jr})=  \sum_{k=1}^K\pi_k\sum_{l=0}^Lw_l^{kr}f_l(\beta_{jr})
%     = \sum_{l=0}^L\eta_{lr}f_l(\beta_{jr}),
% \end{equation}
% where $\eta_{lr}=\sum_{k=1}^K\pi_kw_l^{kr}$. Thus, by (\ref{eq:5}), we get
% \begin{equation}
%     p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr},\pi, g) = \sum_{l=0}^L\theta_{ljr}p_{l}(\beta_{jr}|\hat\beta_{jr},\hat s_{jr}).
% \end{equation}
% The posterior mixture component $p_l$ is the posterior on $\beta_{jr}$ that would be obtained using prior $f_l(\beta_{jr})$ and likelihood $p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})$. To compute the mixture weights $\theta_{ljr}$, denote
% \begin{equation}
%     \tilde f_{ljr}(\hat\beta_{jr}) := \int f_l(\beta_{jr})p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})d\beta_{jr},
% \end{equation}
% the convolution of $f_l$ and a density function. Then $\theta_{ljr}$ can be obtained from
% \begin{equation}
%     \theta_{ljr} = \frac{\eta_{lr}\tilde f_{ljr}(\hat\beta_{jr})}{\sum_{l'=0}^L\eta_{l'r}\tilde f_{l'jr}(\hat\beta_{jr})}.
% \end{equation}
